### 2013-05-31 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
adding relaxation data figures

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/rich_relax_iters.pdf}
  \end{center}
  \caption{\textbf{Number of iterations to converge a single
      eigenvalue iteration of the fuel assembly problem as a function
      of the Richardson relaxation parameter.} \textit{The Neumann
      relaxation parameter was fixed at 1.0 and \sn{3}{4} stochastic
      histories were used to compute the MCSA correction at each
      iteration.}}
  \label{fig:rich_relax_iters}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/rich_relax_time.pdf}
  \end{center}
  \caption{\textbf{CPU time in seconds to converge a single eigenvalue
      iteration of the fuel assembly problem as a function of the
      Richardson relaxation parameter.} \textit{The Neumann relaxation
      parameter was fixed at 1.0 and \sn{3}{4} stochastic histories
      were used to compute the MCSA correction at each iteration.}}
  \label{fig:rich_relax_time}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/neumann_relax_iters.pdf}
  \end{center}
  \caption{\textbf{Number of iterations to converge a single
      eigenvalue iteration of the fuel assembly problem as a function
      of the Neumann relaxation parameter.} \textit{The Richardson
      relaxation parameter was fixed at 1.0 and \sn{3}{4} stochastic
      histories were used to compute the MCSA correction at each
      iteration.}}
  \label{fig:neumann_relax_iters}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/neumann_relax_time.pdf}
  \end{center}
  \caption{\textbf{CPU time in seconds to converge a single eigenvalue
      iteration of the fuel assembly problem as a function of the
      Neumann relaxation parameter.} \textit{The Richardson relaxation
      parameter was fixed at 1.0 and \sn{3}{4} stochastic histories
      were used to compute the MCSA correction at each iteration.}}
  \label{fig:neumann_relax_time}
\end{figure}

>>>>

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/relax_iters.pdf}
  \end{center}
  \caption{\textbf{Number of iterations to converge a single
      eigenvalue iteration of the fuel assembly problem as a function
      of the relaxation parameters.} \textit{The Neumann relaxation
      parameter was fixed at 1.0 and \sn{3}{4} stochastic histories
      were used to compute the MCSA correction at each iteration.}}
  \label{fig:rich_relax_iters}
\end{figure}

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/relax_time.pdf}
  \end{center}
  \caption{\textbf{CPU time in seconds to converge a single eigenvalue
      iteration of the fuel assembly problem as a function of the
      relaxation parameters.} \textit{The Neumann relaxation parameter
      was fixed at 1.0 and \sn{3}{4} stochastic histories were used to
      compute the MCSA correction at each iteration.}}
  \label{fig:rich_relax_time}
\end{figure}
